\documentclass[11pt,a4paper]{article}
\usepackage[margin=0.9in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mdwlist}
\usepackage[hidelinks]{hyperref}
\usepackage{tgpagella}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\pagestyle{empty}
\setlength{\tabcolsep}{0em}

% indentsection style, used for sections that aren't already in lists
% that need indentation to the level of all text in the document
\newenvironment{indentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{#1}}%
	\item[]%
}
{\end{list}}

% opposite of above; bump a section back toward the left margin
\newenvironment{unindentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{-0.5#1}}%
	\item[]%
}
{\end{list}}

% format two pieces of text, one left aligned and one right aligned
\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
	#1 &
	#2 \\
\end{tabular*}}

\newcommand{\Cplusplus}
{C\nolinebreak[4]\hspace{-.05em}\raisebox{.22ex}{\footnotesize\bf ++}}

\begin{document}
{\Large \textbf{Marc-André Servant}}

256 rue de Carignan, Repentigny, Québec, Canada J5Y 4A9

+1-514-641-6011 \ \ -- \ \ \href{mailto:marc.andre3@hotmail.com}{marc.andre3@hotmail.com}
\\

\hrule
\vspace{-0.4em}
\subsection*{Experience}

\begin{itemize}
	\parskip=0.1em

	\item
	\headerrow
		{\textbf{TelcoBridges, Inc.}}
		{\textbf{Boucherville, Canada}}
	\\
	\headerrow
		{\emph{Software Developer, Summer Intern}}
		{\emph{2016}}
	\begin{itemize*}
		\item Software development for the Telcodium server power supply project.
		\item Development of firmware for the embedded microcontroller in the device (in C).
		\item Writing firmware modules to enable the microcontroller to communicate with the host server
		using PMBus / SMBus interfaces.
		\item Writing application for the host server to communicate with its power supply and display
		electrical troubleshooting data (in C/\Cplusplus).
		\item Programming adjustable electrical loads and measuring instruments in order to run automated
		overnight quality control tests.
	\end{itemize*}

	\item
	\headerrow
		{\textbf{TelcoBridges, Inc.}}
		{\textbf{Boucherville, Canada}}
	\\
	\headerrow
		{\emph{Software Developer, Summer Intern}}
		{\emph{2017}}
	\begin{itemize*}
		\item Firmware development for the Telcodium power inverter project.
		\item Experimenting with different control strategies for the inverter using standard electronics laboratory
		equipment and JTAG debugger.
		\item Programming (in C) and debugging of the application and state machine running in parallel with
		the real-time controller.
		\item Development of a fast fault detection algorithm to protect the circuit with real-time constraints
		(in C with some parts in assembly)
	\end{itemize*}

\end{itemize}


\hrule
\vspace{-0.4em}
\subsection*{Education}

\begin{itemize}
	\parskip=0.1em

	\item 
	\headerrow
		{\textbf{École Polytechnique de Montréal}}
		{\textbf{Montreal, Canada}}
	\\
	\headerrow
		{\emph{Computer Engineering}}
		{\emph{2015 -- present}}
	\begin{itemize*}
		\item Grade point average of $3.70/4$
		\item Award of excellence on university transcript
	\end{itemize*}
	
	\item 
	\headerrow
		{\textbf{Cégep régional de Lanaudière à L'Assomption}}
		{\textbf{L'Assomption, Canada}}
	\\
	\headerrow
		{\emph{DEC (pre-college diploma) in Natural Sciences}}
		{\emph{2013 -- 2015}}
	\begin{itemize*}
		\item R score of 32.3 (equivalent to Z-score of $+1.46~\sigma$)
	\end{itemize*}

\end{itemize}

\hrule
\vspace{-0.4em}
\subsection*{Projects}

\begin{itemize}
	\parskip=0.1em

	\item 
	\headerrow
		{\textbf{Flight data recorder for a model rocket}}
		{\emph{2015 (Cegep final project)}}
	\begin{itemize*}
		\item Component selection and construction of an electronic circuit.
		\item Collection of data from various sensors using microcontroller.
		\item Processing of microcontroller data on computer using a Kálmán filter.
		\item Exporting flight altitude and acceleration data to Excel.
	\end{itemize*}

\end{itemize}


\hrule
\vspace{-0.4em}
\subsection*{Skills}

\begin{indentsection}{\parindent}
\hyphenpenalty=1000
\begin{description*}
	\item[Experience working on embedded systems with limited resources]
	\item[Language skills:]
	French (native), English (fluent)
	\item[Proficient in:]
	C, \Cplusplus, HTML, CSS, JavaScript (incl. Node.js)
	\item[Basic knowledge of:]
	Java, Bash shell, PHP, \LaTeX, Python
\end{description*}
\end{indentsection}

\end{document}
